Approximation as Differentiation

### 2025-07-08 main/approx-as-tangents.tex
Fix chain-rule refs.

\begin{remark}[Chain Rule]
  \label{rem:cm-chain-rule}
  It is almost a triviality at this point, but the crucial point is
  that, for any cm functions $f : X \to Y$ and $g : Y \to Z$, the
  restriction maps (``forward derivatives'') compose according to the
  chain rule from \remref{chain-rule}:
  \begin{displaymath}
    (g \circ f)_x = g_{f(x)} \circ f_x
  \end{displaymath}
  We will see this phenomenon repeated in the definition of stable
  functions below.
\end{remark}

@@

\begin{example}[Is Conditional Multiplicativity Enough?]
  \label{ex:non-stable-function}
  An example that is conditionally multiplicative, but does not admit
  a backards map of approximations (from \citet[just
  before Lemma 12.2.3]{amadio-curien}, originally due to Berry) is given by defining
  $\mathrm{unstable} : D \to \{\bot \sqsubseteq \top\}$, where
  $D = \bot \sqsubseteq \cdots \sqsubseteq n \sqsubseteq \cdots
  \sqsubseteq 1 \sqsubseteq 0$, as $\mathrm{unstable}(\bot) = \bot$
  and $\mathrm{unstable}(n) = \top$. This is monotone, and preserves
  meets in every $\downset{x}$. However, there is no ``best'' (i.e.,
  least) input that gives us any finite output.
\end{example}

@@

\begin{remark}[Chain Rule]
  As for the ``forward derivatives'' of conditionally multiplicative
  functions, the forward and backwards parts of a stable function
  compose according to the chain rule (c.f. \remref{chain-rule}):
  \begin{itemize}
  \item $(g \circ f)_x = g_{f(x)} \circ f_x : \downset{x} \linearto \downset{g(f(x))}$
  \item $(g \circ f)^*_x = f*_x \circ g^*_{f(x)} : \downset{g(f(x))} \linearto \downset{x}$
  \end{itemize}
  We will use this property in \propref{embed-stable} to show that
  $\Lposet$ embeds into our category of sets-with-approximation.
\end{remark}

>>>>

\begin{remark}[Chain Rule]
  \label{rem:chain-rule-cm}
  It is almost a triviality at this point, but the crucial point is
  that, for any cm functions $f : X \to Y$ and $g : Y \to Z$, the
  restriction maps (``forward derivatives'') compose according to the
  chain rule from \remref{chain-rule}:
  \begin{displaymath}
    (g \circ f)_x = g_{f(x)} \circ f_x
  \end{displaymath}
  We will see this phenomenon repeated in the definition of stable
  functions below.
\end{remark}

@@

\begin{example}[Is Conditional Multiplicativity Enough?]
  \label{ex:non-stable-function}
  An example that is conditionally multiplicative, but does not admit
  a backwards map of approximations (from \citet[just
  before Lemma 12.2.3]{amadio-curien}, originally due to Berry) is given by defining
  $\mathrm{unstable} : D \to \{\bot \sqsubseteq \top\}$, where
  $D = \bot \sqsubseteq \cdots \sqsubseteq n \sqsubseteq \cdots
  \sqsubseteq 1 \sqsubseteq 0$, as $\mathrm{unstable}(\bot) = \bot$
  and $\mathrm{unstable}(n) = \top$. This is monotone, and preserves
  meets in every $\downset{x}$. However, there is no ``best'' (i.e.,
  least) input that gives us any finite output.
\end{example}

@@

\begin{remark}[Chain Rule]
  \label{rem:chain-rule-stable}
  As for the ``forward derivatives'' of conditionally multiplicative
  functions, the forward and backwards parts of a stable function
  compose according to the chain rule (c.f. \remref{chain-rule}):
  \begin{itemize}
  \item $(g \circ f)_x = g_{f(x)} \circ f_x : \downset{x} \linearto \downset{g(f(x))}$
  \item $(g \circ f)^*_x = f*_x \circ g^*_{f(x)} : \downset{g(f(x))} \linearto \downset{x}$
  \end{itemize}
  We will use this property in \propref{embed-stable} to show that
  $\Lposet$ embeds into our category of sets-with-approximation.
\end{remark}
